### 2010-03-26 docs/architecture/architecture.tex
start documenting the helper modules

To find a particular species, a query can be made through the {\tt network}
module, such as:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
and then the \fab\ can be indexed using {\tt spec\_comp-1+ic12} to
get ``carbon-12''.

@@

@@

@@

The {\tt variables} module provides

>>>>

@@

The {\tt network} module defines the number species advected by the
code ({\tt nspec}), their ordering, and gives their basic properties
(like atomic number, $Z$, and atomic mass, $A$).  All MAESTRO problems
require a {\tt network} module, even if there are no reactions
modeled.  Many different reaction modules (containing different sets
of isotopes) exist in {\tt extern/networks}.  The particular network
used by a problem is defined in the problem's {\tt GNUmakefile}.

@@

{\tt probin\_module} provides access to the runtime parameters.

@@

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are listed in table~\ref{tab:variable_keys}.
\begin{table}[h!]
\centering
\begin{tabular}{ll}
\hline
{\tt rho\_comp}  & density \\
{\tt rhoh\_comp} & density * specific enthalpy, $(\rho h)$ \\
{\tt spec\_comp} & starting index of the species \\
{\tt temp\_comp} & temperature \\
\hline
\end{tabular}
\caption{\label{tab:variable_keys} {\tt variables} module common keys}
\end{table}

To find a particular species, a query can be made through the {\tt
  network} module, such as:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
and then the \fab\ can be indexed using {\tt spec\_comp-1+ic12} to
get ``carbon-12''.
The {\tt variables} module also provides keys for the plotfile
variables and boundary condition types.
